AE Comments

### 2023-05-09 ba_resubmit/third-submission/suggestions/third-revision-review-comments.tex
updated comments from ae.

Note: I do not believe that we should be integrating out the prior distribution. I think we did this at the confusion from the first revision of the  AR. We should instead just update the conditionals to form a Gibbs update, which will make the algorithm justified. If you believe that the algorithm is correct, we will need to convince the AE why it is a valid Markov chain or rather Gibbs update of the partition. 

@@

\textcolor{blue}{It will not be justified unless the full conditionals of the Gibbs sampler contain a sequential update or one proves that this is a justified Gibbs sampler. This was the point that Serge mentioned in his email. Currently, it is not a valid Gibbs sampler. I attempt to explain this more clearly below.}

It would need to be something like this, which comes from Aleshin-Guendel and Steorts (2023). The partition is equivalent to the co-reference matrix or linkage structure. The partition approach is more widely understood by the Bayesian non-parametrics community (or statistics community), which is why we are using this terminology. (They will not easily understand the linkage structure or coreference matrix without connections being made for them).

>>>>

Note: I do not believe that we should be integrating out the prior distribution. I think we did this at the confusion from the first revision of the  AE. We should instead just update the conditionals to form a Gibbs update, which will make the algorithm justified. If you believe that the algorithm is correct, we will need to convince the AE why it is a valid Markov chain or rather Gibbs update of the partition. 

@@

\textcolor{blue}{It will not be justified unless the full conditionals of the Gibbs sampler contain a sequential update or one proves that this is a justified Gibbs sampler. This was the point that Serge mentioned in his email. Currently, it is not a valid Gibbs sampler. I attempt to explain this more clearly below. Looking at Pitman, Pruenster, and the BNP literature, I cannot find a reference regarding why the Markov chain would be valid in this case. If you were to prove this, it would be a new result (to my knowledge).}

It would need to be something like this, which comes from Aleshin-Guendel and Steorts (2023), which extends the general clustering literature. The partition is equivalent to the co-reference matrix or linkage structure. The partition approach is more widely understood by the Bayesian non-parametrics community (or statistics community), which is why we are using this terminology. (They will not easily understand the linkage structure or coreference matrix without connections being made for them).
